---
title: "Exercise1"
author: "Hannah Winter"
format: html
editor: visual
---

### Exercice1 - Part B

First, the *ggplot2* package is imported:

```{r}
library(ggplot2)
```

#### 1. Sampling Values

After sampling 100 values from the log-normal distribution ($\mu$ = 5, $\sigma$ = 0.5), the obtained vector is transformed in a $100*1$ dimensional dataframe.

```{r}
set.seed(10)
sample = rlnorm(100, meanlog = 5, sdlog = 0.5)
df = data.frame(sample)
```

The sampled values have the mean $\mu$ = `r round(mean(sample),3)` and the standard deviation $\sigma$ = `r round(sd(sample),3)`.

### 2. Visualisation

#### 2.1. Creating the Histograms

The library *ggplot2* is used to obtain a graphical representation of the sampled data. First, the histogram of the sample is plotted.

```{r}
ggplot(df, aes(x = sample)) + 
  geom_histogram(color="lightblue", fill="black") + 
  labs(title = "Histogram (linear scale)",
       x = "value",
       y = "count")
```

Next, the scale of the histogram is log-transformed.

```{r}
ggplot(df, aes(x = sample)) + 
  geom_histogram(color="lightblue", fill="black") + 
  labs(title = "Histogram (log scale)",
       x = "value",
       y = "count") + 
  coord_trans(x = "log10")
```

#### 2.2. Creating the Violin-Plot

```{r}
ggplot(df, aes(x = "", y = sample)) + 
  geom_violin(color="black", fill="lightblue") + 
  labs(title = "Violin-Plot (linear scale)",
       x = "sample",
       y = "value")
```
